### 2020-02-27 Article.tex
Clase Albert

\newcommand{\cc}{\mathfrak{c}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Hc}{\mathcal{H}}
\newcommand{\Lan}{\mathcal{L}}
\newcommand{\Ln}{\lim\limits_{n\to \infty}}
\newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
\newcommand{\morph}[1]{\simeq_#1}
\newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
\newcommand{\gnp}{G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1})}
\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
\newcommand{\ehr}{\textsc{Ehr}}

@@

\begin{definition} 
	Given a set $\Sigma$ and an hypergraph $G$, a $\Sigma$-coloring 
	of $G$ is a function $\chi: V(G)\rightarrow \Sigma$. 
	A $\Sigma$-hypergraph $(G,\chi)$ is an hypergraph $G$ equipped
	with a $\Sigma$-coloring of $G$, $\chi$. When $\chi$ is understood
	or is not relevant we may omit it and write just $G$ instead of $(G,\chi)$.\par
	Given two $\Sigma$-hypergraphs $(G_1,\chi_1)$ and $(G_2,\chi_2)$,
	a $\Sigma$-isomorphism between them is an hypergraph isomorphism 
	$f:V(G_1)\rightarrow V(G_2)$ satisfying that
	that for any $v\in V(G_1)$, $\chi_1(v)=\chi_2(f(v))$.
	A $\Sigma$ automorphism of a $\Sigma$-hypergraph $G$ is a 
	$\Sigma$-isomorphism from $G$ to itself.
	\par
	Let $(H,\chi_1), (G,\chi_2)$ be two $\Sigma$-hypergraphs. 
	Then a copy of $H$ in $G$ is
	a sub-hypergraph $G_2\subset G$ such that 
	$(H,\chi_1) \simeq_\Sigma (G_2,\chi_2|_{_{G_2}})$.	\par

	Notation: $Copies([n],(G, \chi))$
	Notation: $H\subset_{\Sigma}G$.

@@

\begin{theorem}
	Let $k\in \N$. For each $i\in [k]$ 
	\begin{itemize}
		\item Let $\Sigma_i$ be a set, let $H_i$ be a unicycle and 
		let $\rho^i$ be a $\Sigma_i$-coloring of $H_i$.
		\item Let $(\chi^i_n)_{n\in\N}$ be a succession of
		random $\Sigma_i$-colorings of $(G_n)_{n\in \N}$
		\item Let $X_{i,n}$ be the random variable that counts
		the number of copies of $(H_i, \rho^i)$ in
		$(G_n,\chi^i_n)$.				
	\end{itemize}
	Let $\mathcal{F}=\{H_1,\dots, H_n\}$. Suppose that the
	successions $(\chi^1_n)_{n\in\N}, \dots, (\chi^k_n)_{n\in\N}$
	are $\mathcal{F}$-independent. Then, for each $a_1,\dots,a_k\in \N$
	\[
	\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k X_{n,i}=a_i  \big)=
	\prod_{i=1}^{k}e^{-\lambda_i}\frac{\lambda_i^{a_i}}{a_i!},
	\]
	where for each $i\in [k]$,
	\[
	\lambda_i:= \frac{\prod_{j\in \sigma} \beta_j^{e_j(H_i)}}{|Aut(H_i,\rho^i)|} 
	\prod_{v\in V(H_i)} \mathrm{Pr}\big[\chi^i=\rho^i(v)\big].
	\]
\end{theorem}
\begin{proof}
	Because of \cref{thm:BrunSieve} we only need to show that for any 
	fixed $b_1,\dots, b_k\in \N$ it is satisfied
	\[
	\Ln \mathrm{E}\big[ \prod_{i=1}^{k} (X_{n,i})_{b_i} \big]=
	\prod_{i=1}^{k} \lambda_i^{b_i}.		
	\]
	For each $n\in \N$ let $\Omega_n$ be the set
	of $b_1, \dots, b_k$-configurations of $(H_1,\rho^1)
	,\dots, (H_k, \rho^k)$ over $[n]$. Then
	\[
	\Ln \mathrm{E}\big[ \prod_{i=1}^{k} (X_{n,i})_{b_i} \big]=
	\Ln \sum_{(O_1,\dots, O_k)\in \Omega_n}
	\mathrm{Pr}
	\big(
	(O_1,\dots, O_k) \subset G_n
	\big).	
	\]
	Let $\Omega^{\times}_n\subset \Omega_n$ be the set of 
	disjoint configurations in $\Omega_n$. Because of REF,
	\[
	\Ln \sum_{(O_1,\dots, O_k)\in \Omega_n}
	\mathrm{Pr}
	\big(
	(O_1,\dots, O_k) \subset G_n
	\big)=
	\Ln \sum_{(O_1,\dots, O_k)\in \Omega^\times_n}
	\mathrm{Pr}\big(
	(O_1,\dots, O_k) \subset G_n
	\big).
	\]
	Because of the symmetry of the random hypergraph $G_n$ and
	the colorings $\chi^1_n, \dots, \chi^k_n$ the probability
	$\mathrm{Pr}\big(
	(O_1,\dots, O_k) \subset G_n
	\big)$ is the same for all $(U_1,\dots, U_k)\in 
	\Omega^\times_n$. Thus, if we fix
	$(O_1, \dots, O_k)$ a 
	disjoint $b_1,\dots,b_k$-configuration of
	 $(H_1,\rho^1)
	,\dots, (H_k, \rho^k)$ over $\N$, 
	\[
	\Ln \sum_{(O_1,\dots, O_k)\in \Omega^\times_n}
	\mathrm{Pr}\big(
	(O_1,\dots, O_k) \subset G_n
	\big) =
	\Ln |\Omega^{\times}_n|	\mathrm{Pr}\big(
	(U_1,\dots, U_k) \subset G_n
	\big).
	\]

@@

>>>>

\newcommand{\cc}{\mathfrak{c}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Hc}{\mathcal{H}}
\newcommand{\Lan}{\mathcal{L}}
\newcommand{\Ln}{\lim\limits_{n\to \infty}}
\newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
\newcommand{\morph}[1]{\simeq_#1}
\newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
\newcommand{\gnp}{G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1})}
\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
\newcommand{\ehr}{\textsc{Ehr}}
\newcommand{\PR}[1]{\mathrm{Pr}\big(#1\big)}

@@

\begin{definition} 
	Given a set $\Sigma$, a $\Sigma$-hypergraph is a pair
	$(G,\chi)$ consisting of an hypergraph $G$ and a map 
	$\chi: V(G) \rightarrow \Sigma$.  
	Given two $\Sigma$-hypergraphs $(H,\rho)$ and $(G,\chi)$,
	an isomorphism between them is an hypergraph isomorphism 
	$f:V(H)\rightarrow V(G)$ satisfying $\rho(v)=\chi(f(v))$
	for any $v\in V(H)$. 
	An automorphism of a $\Sigma$-hypergraph $(G,\chi)$ is an
	isomorphism from $(G,\chi)$ to itself. As with the case of
	hypergraphs we write $Aut(G,\chi)$ to denote the group of 
	automorphisms of $(G,\chi)$.
	\par
	Let $(H,\rho), (G,\chi)$ be two $\Sigma$-hypergraphs. 
	Then a copy of $H$ in $G$ is
	a sub-hypergraph $H^\prime\subset G$ such that 
	$(H,\rho)$ is isomorphic to 
	$(H^\prime,\chi|_{_{H^\prime}})$.\par
	Given a $\Sigma$-hypergraph $(G,\chi)$ and a set $V$ we
	define the set $Copies(S,(G, \chi))$ as the one that contains all 
	possible $\Sigma$-hypergraphs $(H,\rho)$ isomorphic to $(G,\chi)$ 
	such that $V(H)\subset S$.
	Notation: $H\subset_{\Sigma}G$.

@@

\begin{theorem}
	Let $k\in \N$. For each $i\in [k]$ 
	\begin{itemize}
		\item Let $\Sigma_i$ be a set, let $H_i$ be a unicycle and 
		let $\rho^i$ be a $\Sigma_i$-coloring of $H_i$.
		\item Let $(\chi^i_n)_{n\in\N}$ be a succession of
		random $\Sigma_i$-colorings of $(G_n)_{n\in \N}$
		\item Let $X_{i,n}$ be the random variable that counts
		the number of copies of $(H_i, \rho^i)$ in
		$(G_n,\chi^i_n)$.				
	Let $\mathcal{F}=\{H_1,\dots, H_n\}$. Suppose that the
	successions $(\chi^1_n)_{n\in\N}, \dots, (\chi^k_n)_{n\in\N}$
	are $\mathcal{F}$-independent. Then, for each $a_1,\dots,a_k\in \N$
	\[
	\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k X_{n,i}=a_i  \big)=
	\prod_{i=1}^{k}e^{-\lambda_i}\frac{\lambda_i^{a_i}}{a_i!},
	\]
	where for each $i\in [k]$,
	\[
	\lambda_i:= \frac{\prod_{j\in \sigma} \beta_j^{e_j(H_i)}}{|Aut(H_i,\rho^i)|} 
	\prod_{v\in V(H_i)} \mathrm{Pr}\big[\chi^i=\rho^i(v)\big].
	\]
\end{theorem}
\begin{proof}
	Because of \cref{thm:BrunSieve} we only need to show that for any 
	fixed $b_1,\dots, b_k\in \N$ it is satisfied
	\[
	\Ln \mathrm{E}\big[ \prod_{i=1}^{k} (X_{n,i})_{b_i} \big]=
	\prod_{i=1}^{k} \lambda_i^{b_i}.		
	\]
	For each $n\in \N$ let $\Omega_n$ be the set
	of $b_1, \dots, b_k$-configurations of $(H_1,\rho^1)
	,\dots, (H_k, \rho^k)$ over $[n]$. Then
	\[
	\Ln \mathrm{E}\big[ \prod_{i=1}^{k} (X_{n,i})_{b_i} \big]=
	\Ln \sum_{(O_1,\dots, O_k)\in \Omega_n}
	\mathrm{Pr}
	\big(
	(O_1,\dots, O_k) \subset G_n
	\big).	
	\]
	Let $\Omega^{\times}_n\subset \Omega_n$ be the set of 
	disjoint configurations in $\Omega_n$. Because of REF,
	\[
	\Ln \sum_{(O_1,\dots, O_k)\in \Omega_n}
	\mathrm{Pr}
	\big(
	(O_1,\dots, O_k) \subset G_n
	\big)=
	\Ln \sum_{(O_1,\dots, O_k)\in \Omega^\times_n}
	\mathrm{Pr}\big(
	(O_1,\dots, O_k) \subset G_n
	\big).
	\]
	Because of the symmetry of the random hypergraph $G_n$ and
	the colorings $\chi^1_n, \dots, \chi^k_n$ the probability
	$\mathrm{Pr}\big(
	(O_1,\dots, O_k) \subset G_n
	\big)$ is the same for all $(U_1,\dots, U_k)\in 
	\Omega^\times_n$. Thus, if we fix
	$(O_1, \dots, O_k)$ a 
	disjoint $b_1,\dots,b_k$-configuration of
	 $(H_1,\rho^1)
	,\dots, (H_k, \rho^k)$ over $\N$, 
	\[
	\Ln \sum_{(O_1,\dots, O_k)\in \Omega^\times_n}
	\mathrm{Pr}\big(
	(O_1,\dots, O_k) \subset G_n
	\big) =
	\Ln |\Omega^{\times}_n|\cdot \mathrm{Pr}\big(
	(U_1,\dots, U_k) \subset G_n
	\big).
	\]
	Let $S$ be the underlying set of the configuration $(U_1,\dots,U_k)$.
	Let $l= \sum_{H\in S} v(S)$. Then it is satisfied 
	\[
	|\Omega^{\times}_n|= \frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}.
	\]
	Using the definition of $(U_1,\dots, U_k) \subset G_n$ and
	substituting $|\Omega^{\times}_n|$ we get
	\[
	\Ln |\Omega^{\times}_n|\cdot \mathrm{Pr}\big(
	(U_1,\dots, U_k) \subset G_n
	\big) = \Ln
	\frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}\cdot
	\PR{\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
	(H,\rho)\subset (G_n, \chi_n^i)}.
	\]
	But the event $(H,\rho)\subset (G_n, \chi_n^i)$ is equivalent to $H\subset G_n$ and
	$\chi_n^i(v)=\rho(v)$ for all $v\in V(H)$. Thus the LHS of last equation equals
	\[
	\Ln
	\frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}\cdot
	\Pr\Big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
	\big(H\subset G_n \bigwedge_{v\in V(H)} \chi_n^i(v)=\rho(v) \big) \Big).
	\]
	For each $n\in \N$ let $A_n$ the event
	\[
	A_n:=\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
	H\subset G_n.
	\]	
	Then,
	\begin{align*}
	&\Pr\Big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
	\big(H\subset G_n \bigwedge_{v\in V(H)} \chi_n^i(v)=\rho(v) \big) \Big)=\\
	&\Pr\big(A_n\big)\cdot \Pr\big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
	\bigwedge_{v\in V(H)} \chi^i_n(v)=\rho(v) \, \big| \, A \big).
	\end{align*}
	It holds that
	\[
	\PR{A_n}=\frac{1}{n^l} \prod_{i=1}^{k}\prod_{R\in \sigma} \beta_R^{e_R(H_i)\cdot b_i},
	\]
	and in consequence 
	\[
	\Ln \frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}\cdot \PR{A_n}
	= \frac{\prod_{i=1}^{k}\prod_{R\in \sigma} \beta_R^{e_R(H_i)\cdot b_i}}
	{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}.
	\]
	Finally, using the hypothesis that 
	$(\chi^1_n)_{n\in\N}, \dots, (\chi^k_n)_{n\in\N}$
	are $\mathcal{F}$-independent we obtain
	\[
	\Ln \Pr\big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
	\bigwedge_{v\in V(H)} \chi^i_n(v)=\rho(v) \, \big| \, A \big)
	= \prod_{i=1}^{k} \prod_{v\in V(H_i)} \Pr\big[ \chi^i=\rho^i(v)\big]^{b_i}.
	\]
	The result follows from joining equations. 

@@

\begin{definition}
	Let $\Sigma$ be a set containing the empty label $\emptyset$.
	Let $V\subset [n]$. We say that a random $\Sigma$-coloring $\chi$
	of $G_n$ is $V$-symmetric if $\chi(v)=\emptyset$ if and only if $v\in V$ and
	for any $s\in \Sigma$ the probability $\Pr(\chi(v)=s)$ is the same for all 
	$v\in [n]\setminus V$. \par
	Let $V\subset \N$ be a finite set of vertices and let $(\chi^n)_{n\in \N}$
	be a succession such that each $\chi^n$ is a random coloring of $G_n$. We
	call the succession $(\chi^n)_{n\in \N}$ $V$-regular if each $\chi^n$ is
	$V$-symmetric and for all $s\in \Sigma$ and $v\in \N \setminus \N$ the limit 
	$\Ln \PR{\chi^n(v)=s}$ exists. 
\end{definition}

\begin{definition}
	Let $\Sigma$ be a set containing the empty label $\emptyset$. A rooted $\Sigma$-edge
	is a $\Sigma$-hypergraph $(e,\chi)$ where $e$ is an edge 
	(i.e., an hypergraph consisting of only one edge), $v\in V(e)$ is a vertex called the root 
	of $e$, and $\chi: V(e)\rightarrow \Sigma$ such that $\chi(u)=\emptyset$ if and only if 
	$u=v$.\par
	Given a rooted $\Sigma$-edge $(e,v,\chi)$, a set $V$ and a 
\end{definition}

\begin{definition}
